Analysis of Climate Sensitivity using HadAM3

### 2014-04-27 article.tex
Add some info to IPCC links.
Add in the South America correlation plots.
All figures being added to results.

% Rem: \lp
% Analysing_your_runs
% Converting_UM_files
% Course_work_guide
% geogg134merit
% geogg134pass
% Setting_up_your_runs
% marengoInternal
% WG1AR5_ALL_FINAL
% WG1AR5_AnnexI_FINAL
% WG1AR5_Chapter02_FINAL
% WG1AR5_Chapter06_FINAL
% WG1AR5_Chapter08_FINAL
% WG1AR5_Chapter09_FINAL
% WG1AR5_Chapter14_FINAL
% WG1AR5_SPM_FINAL
% WG1AR5_TS_FINAL
% SREX-All_FINAL
% RCP_Guide
% SREX-Ch3-Supplement_FINAL

@@

% Layout the groundwork for why studying CO2 is important:
Since 1958 the level of \ce{CO2} in the atmosphere has been monitored at the Mauna Loa observatory in Hawaii (TODO: cite). Its current level now stands at \SI{401}{ppm} (April, 2014), having increased from a value of \SI{315}{ppm} since 1958, which was already over the maximum value of \ce{CO2} that the Earth had seen for the previous \SI{800 000}{years} (TODO: cite). It is a well mixed gas, so its value at on location is indicative of its value across the globe, although there are regional variations (TODO: cite). It is a Greenhouse Gas (GHG), meaning that it is transparent to the majority of short-wave radiation incident on the Earth from the Sun, but opaque to the outgoing long-wave radiation, which has the effect of heating up the Earth's surface (TODO: cite Neelin). It is ``very likely'' that it is responsible for the recent global rise in temperatures (TODO: cite: IPCC), which in turn are predicted to lead to increased intensity of tropical cyclones (TODO: cite), droughts (TODO: cite) and extreme precipitation events (TODO: cite). It is therefore of vital importance that its effect on the Earth's climate is studied, so as the consequences of releasing more \ce{CO2} into the atmosphere can be predicted without performing the actual experiment.

@@

\begin{figure}[hbp]
    \centering
    \includegraphics[width=\textwidth]{figures/figure_1}
    \caption{Caption.}
    \label{fig:figure_1}
\end{figure}

>>>>

% Rem: \lp
% Analysing_your_runs
% Converting_UM_files
% Course_work_guide
% geogg134merit
% geogg134pass
% Setting_up_your_runs
% marengoInternal
% WG1AR5_ALL_FINAL
% WG1AR5_AnnexI_FINAL
% WG1AR5_Chapter02_FINAL: Observations: Atmosphere and Surface
% WG1AR5_Chapter06_FINAL: Carbon and Other Biogeochemical Cycles
% WG1AR5_Chapter08_FINAL: Antrhopogenic and Natural Radiative Forcing
% WG1AR5_Chapter09_FINAL: Evaluation of Climate Models
% WG1AR5_Chapter14_FINAL: Climate Phenomena and their Relevance for Future Regional Climate Change
% WG1AR5_SPM_FINAL
% WG1AR5_TS_FINAL
% SREX-All_FINAL
% ar4_wg1_full_report
% RCP_Guide
% SREX-Ch3-Supplement_FINAL

@@

% Layout the groundwork for why studying CO2 is important:
Since 1958 the level of \ce{CO2} in the atmosphere has been monitored at the Mauna Loa observatory in Hawaii (TODO: cite). Its current level now stands at \SI{401}{ppm} (April, 2014), having increased from a value of \SI{315}{ppm} since 1958, which was already over the maximum value of \ce{CO2} that the Earth had seen for the previous \SI{800 000}{years} (TODO: cite). It is a well mixed gas, so its value at on location is indicative of its value across the globe, although there are regional variations (TODO: cite). It is a Greenhouse Gas (GHG), meaning that it is mostly transparent to the short-wave radiation incident on the Earth from the Sun, but opaque to the outgoing long-wave radiation, which has the effect of heating up the Earth's surface (TODO: cite Neelin). It is ``very likely'' that it is responsible for the recent global rise in temperatures (TODO: cite: IPCC), which in turn are predicted to lead to increased intensity of tropical cyclones (TODO: cite), droughts (TODO: cite) and extreme precipitation events (TODO: cite). It is therefore of vital importance that its effect on the Earth's climate is studied, so as the consequences of releasing more \ce{CO2} into the atmosphere can be predicted without performing the actual experiment.

@@

\begin{figure}[hbp]
    \centering
    \includegraphics[width=\textwidth]{figures/global_temp_precip}
    \caption{Caption.}
    \label{fig:global_temp_precip}
\end{figure}

\begin{figure}[hbp]
    \centering
    \includegraphics[width=\textwidth]{figures/sa_seasonal}
    \caption{Caption.}
    \label{fig:sa_seasonal}
\end{figure}

\begin{figure}[hbp]
    \centering
    \includegraphics[width=\textwidth]{figures/sa_diff}
    \caption{Caption.}
    \label{fig:sa_diff}
\end{figure}

\begin{figure}[hbp]
    \centering
    \includegraphics[width=\textwidth]{figures/corr}
    \caption{Caption.}
    \label{fig:corr}
\end{figure}
